---
title: "Merge results for analysis"
output: html_notebook
author: "Federico Saltarin"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
---
<br>
<br>
<br>
<br>
First we import all libraries
```{r}
library(dplyr)
library(data.table)
library(stringr)
library(tcltk)
```
<br>
<br>
Here you can specify the name of your output CSV file 
```{r}
output_file = "Summary_Merged.csv"
```
<br>
<br>
Here you can interactively choose the directory in which all your results are stored and it will create a list of all .csv files
```{r}
directory =  tk_choose.dir(caption = "Select summaries folder: ")
filenames = list.files(path= directory , pattern="*.csv")
```
<br>
<br>
Now all files are merged into a single dataframe and the "Slice" column is modified to remove all spaces and make it more readable.
Moreover, 3 new columns are created:
-Well containing the well name 
-Fov containing the specific number of the FOV
-Slice_N that specifies the slice per every row
This information are taken from the "Slice" column with regular expression pattern matching.
```{r}
fullpath = file.path(directory,filenames)
dataset = do.call("rbind",lapply(fullpath,FUN=function(files){ read.csv(files)}))

dataset = dataset %>% mutate(Slice = str_replace_all(Slice, fixed(" "), "") ) %>% 
                      mutate(Slice = gsub('[(]', "_",  Slice)) %>% 
                      mutate(Slice = gsub('[)]', "_",  Slice)) %>%
                      mutate(Slice = gsub("- ", "",  Slice)) %>% 
                      mutate(Slice = gsub(" ", "_",  Slice)) %>% 
                      mutate(Well = str_extract(string = Slice, pattern = (".*(?=_fld)"))) %>% 
                      mutate(Fov = as.numeric(str_extract(string =  Slice, pattern = ("(?<=fld).*(?=wv)"))) ) %>% 
                      mutate( Slice_N = as.numeric(str_extract(string =  dataset$Slice, pattern = ("(?<=time).*(?=-)"))))
```
<br>
<br>
Now you are asked to select your Experimental Description File (contatining paired well-condition description)
Then the "Condition" column is added to the dataset, based on the information given on your selected file.
```{r}
Data_Exp_Descr = read.csv(tk_choose.files(caption = "Select experimental description file: "))
dataset$Cond_ID = max.col(sapply(Data_Exp_Descr$Well, grepl, dataset$Slice))
dataset$Condition = Data_Exp_Descr$Condition[dataset$Cond_ID]
```
<br>
<br>
A new dataframe is generated, removing not needed columns and modifying the "Well" columns removing the dash.
```{r}
Data = dataset %>%  select(-c(Mean,Cond_ID)) %>%  
                    rename(Slice_ID = Slice,  Slice = Slice_N) %>% 
                    mutate(Well = gsub("-", "", Well))
```
<br>
<br>
Here we check the "head" of the resulting dataframe
```{r}
head(Data)

```

At this point your data is ready to be plotted and here we save the dataframe as a CSV file (using the name specified before)
```{r}
 write.csv(Data, output_file)
```



